% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Paul Woolcock}
% \address used twice to have two lines of address
\address{1450 Schafer Drive, Burton, MI 48509}
\address{(810) 412-8642 or (810) 931-1631}

 
\begin{resume}
 
\section{OBJECTIVE}       A position in the field of computers with special 
                interests in business applications programming, 
                information processing, and management systems. 
 
 
\section{EDUCATION} {\sl Bachelor of Science,} Computer Science \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                University of Michigan-Flint, Flint, MI \\
                expected May 2012 \\
                Concentration: Software Engineering \\
                Minor: Mathematics

                {\sl Bachelor of Arts,} Music \\
                Alma College, Alma, MI \\
                May 2005 \\
                Concentration: Classical Guitar


\section{COMPUTER \\ SKILLS}
{\sl Languages \& Frameworks:} 
Python,
PHP,
HTML/CSS,
Javascript,
Java,
Ruby,
ASP.Net (C\# and Visual Basic),
XSLT/XPath,
Perl,
PL/SQL
CakePHP,
Django,
Ruby on Rails \\

{\sl Software:} 
SQL Server,
MySQL,
PostgreSQL,
Oracle,
CoSign,
Vim,
Git,
Subversion,
Interwoven Teamsite,
VeerWest FormAssembly,
Wordpress,
Apache httpd,
Apache Tomcat,
Microsoft IIS,
Nginx \\

{\sl Operating Systems:} Windows (7, Vista, XP), Mac OSX, Linux

\section{EXPERIENCE} {\sl Web Software Developer } \hfill September 2009 - Present \\
                University of Michigan-Flint, 
                Information Technology Services, Flint, MI
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                    \item Implemented a custom Events Management solution that
                          allows the Academic Advising and Career Center to
                          more easily manage their Career Fair events.
                    \item Provided support and training for users of Interwoven
                          Teamsite, the campus's Content Management System.
                    \item Developed Java/XSLT components for Interwoven Livesite, the
                          Content Management System the campus is moving to.
                    \item Developed an E-Commerce solution for selling software
                          to students, faculty, and staff on campus.
                    \item Implemented a Microsoft SharePoint 2010 system across
                          campus, and held training sessions for users.
                \end{itemize}

                {\sl Computer Consultant - Web Student } \hfill February 2009 - September 2009 \\
                University of Michigan-Flint,
                Information Technology Services, Flint, MI
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                     \item
                 \end{itemize}

                {\sl Helpdesk Technician} \hfill June 2008 - August 2009 ??? \\
                Genesee County Community Mental Health, \\
                Information Technology Department, Flint, MI
                  \begin{itemize}
                       \item
                   \end{itemize}

\section{REFERENCES}  Organized and directed the 1988 and 1989 Grand 
                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
                charity event to benefit the Troy Boys Club. Over 
                250 people participated each year. 


\end{resume}
\end{document}







